---
title: "HuynhSinghviFinal2"
author: "Aaron Huynh"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r message=FALSE}
#PACKAGES
library(Stat2Data)
library(leaps)
library(HH)
library(readr)
```

## DATA

```{r message=FALSE}
stats = read_csv("csv/nba_team_stats_00_to_21.csv")
stats = stats[-c(1:7,9:17,20:21,28,29)]
```

## SCATTERPLOT MATRIX

```{r out.width="400px"}
pairs(stats, pch=20)
```

## ORIGINAL MODEL

```{r message=FALSE}
#ORIGINAL MODEL
full=lm(PTS~.,data=stats)
summary(full)
```

## ORIGINAL MODEL SUMMARY

PTS = 16.79631 + 0.17396(OREB) + 2.11536(DREB) - 0.95330(TOV) + 1.84086(STL) - 0.28658(BLK) - 0.42277(BLKA) + 0.71571(PF) + 0.21474(PFD)


Max Residual: 13.0809

Median Residual: -0.0344

Min Residual: -11.8620

Adjusted R-squared:  0.6642

## FORWARD SELECTION

```{r}
#FORWARD
none=lm(PTS~1,data=stats)
MSE=(summary(full)$sigma^2)
model = step(none,scope=list(upper=full),scale=MSE,direction="forward")
qqnorm(model$residuals)
summary(model)
```

## FORWARD SELECTION SUMMARY

PTS = 17.74716 + 2.07781(DREB) + 0.21408(PFD) + 1.79778(STL) - 1.04321(TOV) + 0.73092(PF)

Add order: DREB + PFD + STL + TOV + PF

Not included: BLKA, BLK, OREB

Final cP: 7.6182 (close to k+1)

Max Residual: 13.2867

Median Residual: -0.0811

Min Residual: -11.5661

Adjusted R-squared: 0.6633

## BACKWARD ELIMINATION

```{r}
#BACKWARD 
full=lm(PTS~.,data=stats)
MSE=(summary(full)$sigma^2)
step(full,scale=MSE,direction="backward")
qqnorm(model$residuals)
summary(model)
```

## BACKWARD ELIMINATION SUMMARY

PTS = 17.74716 + 2.07781(DREB) + 0.21408(PFD) + 1.79778(STL) - 1.04321(TOV) + 0.73092(PF)

Removed: OREB, BLK, BLKA

Final cP: 7.6182 (close to k+1)

Max Residual: 13.2867

Median Residual: -0.0811

Min Residual: -11.5661

Adjusted R-squared: 0.6633

## STEPWISE REGRESSION

```{r}
full=lm(PTS~.,data=stats)
none=lm(PTS~1,data=stats)
MSE=(summary(full)$sigma^2)
step(none,scope=formula(full),scale=MSE)
qqnorm(model$residuals)
summary(model)
```

## STEPWISE REGRESSION SUMMARY

Same as forward selection

## BEST SUBSETS 

```{r}
all=regsubsets(PTS~.,data=stats)
summaryHH(all)
```